Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution

### 2018-02-14 main.tex
now compiles again
revisions to section 4

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background (see \citep{GrackleMethod} for more details of this implementation). We assume \ion{He}{1} ionization generally follows \ion{H}{1}. This allows us to approximate \ion{He}{1} self-shielding using the same form (A. Rahmati, private communication). We ignore \ion{He}{2} photoionization from the UV background entirely. Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from Cloudy (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \texttt{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

@@

We assume the galaxy is mostly optically thin to stellar FUV and use only local approximations for shielding.  We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
\begin{equation}
\label{eq:PE}
\Gamma_{\rm pe} = (1.3 \times 10^{-24} \mbox{~erg~s~cm}^{-3}) \epsilon n_{\rm H} G_{\rm eff} D 
\end{equation}
where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\rm{exp}(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust to gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}. Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.

@@

\section{Results}
\label{sec:results}
We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first 500~Myr after the first star forms. Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle forms, which is 43~Myr after the actual initialization of the simulation. The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy.

@@

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation (0, 150, 300, and 500 Myr). In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points. Towards the end of the simulation time, the half light radius is $390 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.

The increased gravitational potential towards the center of our dwarf galaxy leads to an inside-out star formation evolution, whereby star formation propagates from the inner regions outward during the galaxy's evolution. This is obvious in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds. This region quickly becomes volume-filled with both warm and hot gas generated from radiation feedback and supernovae respectively. Both the ISM and the halo gas is multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident by the temperature slices in both panels. The ISM properties are quantified further in Section~\ref{sec:phase}.

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0 Myr, 150 Myr, 300 Myr, and 500 Myr. Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single black dot.}
\label{fig:panel_x}
\end{figure*}

The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}. This figure shows the 40~Myr time averaged scale height of all gas in the disk centered on the given time. Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights between 50--200~pc. Although the disk remains thin beyond the stellar radius of our galaxy (a scale height of around 40~--~60~pc), it is resolved at all radii. By the end of the simulation, the majority of the gas has a scale height of $\sim$100~pc. Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging. For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100 - 200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
%We additionally compute the mass weighted height of the disk, defined as $H = (\sum{Mz^2}/\sum{M})^{1/2}$, where the summation is over each gas cell, as a function of radius (not shown here). $H$ is generally larger than the scale height by a factor of 2, but is comparable to the scale height at radii with ongoing star formation, indicating a particularly uniform-then-truncated density distribution. At large radii, away from active star formation, $H$ is roughly 50 pc, or $\sim$ 3 times the scale height.

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on projections/slices.}
\label{fig:panel_z}
\end{figure*}

Interestingly, there is significant structure well above the gas disk in the form of dense clouds and filamentary features, as seen in the edge-on projections. These cold gas clumps appear to have typical sizes on order of $\sim$ 10 pc, but with lower density tails that can extend up to 100 pc. These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy. These clumps have typical velocities on order of a few to tens of kilometers per second, and appear to survive for 10--100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk. The evolution of these dense clumps in the context of the disk-halo interface in our low mass dwarf galaxy will be examined in a future work. 
% AE (left out): This is exciting given recent \citep[e.g.][]{Zheng2017} and ongoing \citep{Zheng2017HST} observational observational work examining the disk-halo interface in nearby galaxies.

@@

We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between $2---4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly this level for 100 Myr, and drops to an average of about $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations. By the end of the simulation, the SFR is very low and infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$. The SNR tracks the SFR with a time delay, with roughly one core collapse supernovae per 100 M$_{\odot}$ of star formation. Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 9.93 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$. We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.

%mm \footnote{  [This is rather too long for a footnote, I think.]
The granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured. Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$. For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$. Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense. Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $6 \times 10^5$ M$_{\odot}$, or roughly 17\%, of the total mass in the galaxy's disk. The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\% and is about equal with the HI gas. This is because the total amount of mass in the disk decreases through feedback driven winds, but the H$_2$ is preferentially retained. Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{sfr_snrx100}
\includegraphics[width=0.475\linewidth]{mass_evolution}
\caption{Left: The SFR and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left). Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time. Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and supernova rate.}
% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
\label{fig:sfr_mass_evolution}
\end{figure*}

\subsection{Phase Diagrams and ISM Properties}
\label{sec:phase}

Our simulations contain both ample resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy. We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM). We emphasize that the molecular ISM phase is defined as all regions with f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content as decoupled from the rest of the gas. See Appendix \ref{appendix:phases} for a quantitative definition of these phases. Each of these phases exist throughout our simulation, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and diffuse and shock heating from stellar feedback throughout the galaxy's evolution. Here we discuss the phase properties of the gas within the inner halo of our dwarf galaxy.

Figure~\ref{fig:phase} shows the temperature-density phase diagram of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300 -- 350~Myr. One can readily identify the two most massive regions of gas in the simulation, a low density, warm phase produced through ionization and supernovae heating, and a cold, high density phase which makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}). Several notable features of the phase diagram include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium. We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results. The boxed regime in the lower right corner shows our star formation density and temperature threshold. Gas in this regime is rapidly consumed by star formation and subsequent feedback. Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does show up in this time average. We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work.

@@

The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}. At this point the molecular component dominates through the end of the simulation.

Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining dominated by the WNM. While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume fraction. However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}. In short, they find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few. The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future works.

@@

To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the \ion{H}{1} ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 200~Myr. This diagram shows how dramatic the increase in ISRF near young, massive stars (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower. The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps). From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy various greatly over time and space in a way that cannot be appropriately captured by an analytic profile. Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation. In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency. It is unclear which of these two modes of feedback is more important in controlling star formation.

@@

\secton{Discussion}
\label{sec:discussion}

@@

\item A thin, yet resolved, gas scale height ($\sim$~50~pc) beyond our stellar radius, with larger scale heights ($\sim 100 - 200$~pc) driven by feedback interior to the stellar radius. This is comparable to the resolution limit of the diffuse HI in observed, gaseous UFDs. See Figure~\ref{fig:scale_height}.

@@

\item Our galaxy forms a significant amount of H$_2$ through gas ($H^-$) reactions. This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy. This leads to high molecular gas fractions, with a H$_2$ mass comparable to the HI content by the end of the simulation. This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies. See Figure~\ref{fig:ISM_evolution}.
\end{enumerate}

>>>>

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}. We assume \ion{He}{1} ionization generally follows \ion{H}{1}. This allows us to approximate \ion{He}{1} self-shielding using the same form (A. Rahmati, private communication). We ignore \ion{He}{2} photoionization from the UV background entirely. Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from Cloudy (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \texttt{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

@@

We assume the galaxy is mostly optically thin to stellar FUV and use only local approximations for shielding.  We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
%mm2
    {\bf Shouldn't the units here include s$^{-1}$ rather than s?}
\begin{equation}
\label{eq:PE}
\Gamma_{\rm pe} = (1.3 \times 10^{-24} \mbox{~erg~s~cm}^{-3})\, \epsilon n_{\rm H} G_{\rm eff} D 
\end{equation}
where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust to gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}. Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.

@@

\section{Results}
\label{sec:results}
We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first star forms. Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle forms, which is 43~Myr after the actual initialization of the simulation. The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy.

@@

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
%mm2 [redundant with caption] Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation (0, 150, 300, and 500 Myr). In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points. 
%
These Figures show 
%mm2 increased gravitational potential towards the center of our dwarf galaxy leads to [can we demonstrate this?  Otherwise it seems like an unsupported claim, since it could have to do with other things like the surface density profile, the rotational velocity profile, etc.]
inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution. This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
%mm2 This region quickly becomes volume-filled with both 
    This central region quickly fills with
warm and hot gas generated from radiation feedback and supernovae respectively. Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels. The ISM properties are quantified further in Section~\ref{sec:phase}.

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation. Shown are the density weighted projection of number density (top row), temperature slices (second row), 
%mm2 and integrated projections giving 
\ion{H}{1} column density (third row), and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single black dot.}
\label{fig:panel_x}
\end{figure*}

The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}. This figure shows the scale height of all gas in the disk, averaged over 40~Myr periods centered on each given time. Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--200~pc. 
%mm2 [moved from above]
  Towards the end of the simulation time, the half-light radius is $390 \pm 21$ pc, where the 
  uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
Although the disk remains thin beyond the half-light radius, with a scale height of around 40--60~pc, it is fully resolved at all radii. By the end of the simulation, the majority of the gas has a scale height of $\sim$100~pc.

Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging. For Leo P, located at 1.7~Mpc, \ion{H}{1} observations that are capable of detecting the diffuse \ion{H}{1} throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest \ion{H}{1} clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
%We additionally compute the mass weighted height of the disk, defined as $H = (\sum{Mz^2}/\sum{M})^{1/2}$, where the summation is over each gas cell, as a function of radius (not shown here). $H$ is generally larger than the scale height by a factor of 2, but is comparable to the scale height at radii with ongoing star formation, indicating a particularly uniform-then-truncated density distribution. At large radii, away from active star formation, $H$ is roughly 50 pc, or $\sim$ 3 times the scale height.

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on views.}
\label{fig:panel_z}
\end{figure*}

Interestingly, there is significant structure well above the gas disk in our model, in the form of dense clouds and filamentary features, as seen in the edge-on projections. These cold gas clumps appear to have typical sizes on order of $\sim 10$~pc, but with lower density tails that can extend up to 100 pc. These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy. These clumps have typical velocities on order of a few to tens of kilometers per second, and appear to survive for 10--100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk. The evolution of these dense clumps in the context of the disk-halo interface in our low mass dwarf galaxy will be examined in a future work. 
% AE (left out): This is exciting given recent \citep[e.g.][]{Zheng2017} and ongoing \citep{Zheng2017HST} observational observational work examining the disk-halo interface in nearby galaxies.

@@

We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between 2--4$ \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly at this level for 100 Myr, and then drops to an average of about
%mm2
  {\bf [Shouldn't this be $4 \times 10^{-5}$?]}
 $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations. By the end of the simulation, the SFR is very low and 
%mm2
   star formation events are
infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$. The SNR tracks the SFR with a time delay, with roughly one core collapse supernovae per 100 M$_{\odot}$ of star formation. Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 9.93 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$. We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.

%mm \footnote{  [This is rather too long for a footnote, I think.]
We note that the granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured. Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$. For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$. Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense. Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $6 \times 10^5$ M$_{\odot}$, or roughly 17\%, of the total mass in the galaxy's disk. The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\% and is about equal with the \ion{H}{1} gas. This is because the total amount of mass in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained. Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{sfr_snrx100}
\includegraphics[width=0.475\linewidth]{mass_evolution}
\caption{Left: The SFR and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left). Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time. 
%mm2 Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and supernova rate.
   Note that the supernova rate has been scaled by a factor of 100 to fit on the same vertical 
   axis as the SFR.}
% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
\label{fig:sfr_mass_evolution}
\end{figure*}

%mm2 \subsection{Phase Diagrams and ISM Properties}
\subsection{ISM Properties}

\label{sec:phase}

Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy. We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM). We emphasize that the molecular ISM phase is defined as all regions with f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content as decoupled from the rest of the gas. See Appendix \ref{appendix:phases} for a quantitative definition of these phases. Each of these phases exist throughout our simulation, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and 
%mm2 diffuse 
  radiative
and shock heating from stellar feedback throughout the galaxy's evolution. Here we discuss the %mm phase
   thermodynamic 
properties of the gas within the inner halo of our dwarf galaxy.

Figure~\ref{fig:phase} shows the temperature-density 
%mm2 phase diagram 
    distribution
of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr. One can readily identify the two
%mm2  most massive regions of gas [eliminated phase language below for consistency with your claim a bit further down the para that there are not well-defined phases.]
    regimes containing most of the mass 
in the simulation: low density, warm gas produced through ionization and supernova heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}). Several notable features of the 
%mm2 phase diagram 
     distribution
include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium. We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results. The boxed regime in the lower right corner shows our star formation density and temperature threshold. Gas in this regime is rapidly consumed by star formation and subsequent feedback. Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does show up in this time average. We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work.

@@

The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}. After this point, the molecular component dominates through the end of the simulation.

Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining dominated by the WNM. While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume fraction. However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}. They find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few. The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future works.

@@

To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the \ion{H}{1} ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 200~Myr. This diagram shows how dramatic the increase in ISRF near young, massive stars (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower. The striking contrast between the two diagrams is due to the shielding of the \ion{H}{1} ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps). From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy various greatly over time and space in a way that cannot be appropriately captured by an analytic profile. Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation. In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency. It is unclear which of these two modes of feedback is more important in controlling star formation.

@@

\section{Discussion}
\label{sec:discussion}

@@

\item A thin, yet resolved, gas scale height ($\sim$~50~pc) beyond our stellar radius, with larger scale heights ($\sim 100 - 200$~pc) driven by feedback interior to the stellar radius. This is comparable to the resolution limit of the diffuse \ion{H}{1} in observed, gaseous UFDs. See Figure~\ref{fig:scale_height}.

@@

\item Our galaxy forms a significant amount of H$_2$ through gas ($H^-$) reactions. This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy. This leads to high molecular gas fractions, with a H$_2$ mass comparable to the \ion{H}{1} content by the end of the simulation. This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies. See Figure~\ref{fig:ISM_evolution}.
\end{enumerate}
